### 2016-11-15 conclusion.tex
Added some conclusion text

>>>>

\section{Results in Context}
Developing a versatile, accurate, resolution insensitve model for feedback has
been a challenge in galaxy simulations for decades.  While a number of recent
models have been developed that are able to produce galaxies which match some
observables, all of these models have relied on purely numerical features to
enhance the effectiveness of feedback and counter the effects of limited
resolution.  The \citet{Keller2014} presented in Chapter 2 is the first model of
its kind that uses a first-principles approach to prevent overcooling.  Beyond
merely ``sufficient'' feedback, the superbubble model also incorporates physics
that previously have been omitted.  Thermal evaporation is a key process for
mixing cold ISM with hot feedback ejecta.  Prior to \citet{Keller2014}, this
process was completely ignored, and the local mass-loading of feedback was set
purely as a numerical parameter.

As we showed in \citet{Keller2015}, including thermal evaporation in simulations
of a Milky Way like galaxy will drastically change the effectiveness of
SN-driven galactic winds.  Removing gas from the galaxy is the only effective
mechanism for regulating star formation on cosmic timescales.  To prevent the
formation of bulges larger than the ones seen in the local universe, bulge
forming gas (low-angular momentum gas) must be removed from the ISM; because
SN-driven winds are most effective at high redshift, when this material is
mostly accreted, the outflows driven from the galaxy preferentially remove
bulge-forming gas.  An important conclusion of this study is that much of the
past work showing that SN feedback was unable regulate star formation without
the addition of ``early feedback'' from radiation pressure, stellar winds, or
photoionization was likely underestimating the effectiveness of SN.  Since many
of these studies used simpler, more numerically-sensitive feedback models that
also omitted thermal evaporation, they were unable to effectively drive the
correct amount of mass into hot, high entropy gas that could leave the galaxy.
This study tells us that the disc-dominant morphology and low stellar fraction
in galaxies like our own all arise from the same mechanism:  heavily mass
loaded, high redshift winds.
